Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project

### 2020-09-11 awipev-CO2.Rmd
changed reading file atm pCO2

```{r atmospheric CO2 Zeppelin, echo=FALSE, message= FALSE, warning=FALSE}
## Atmospheric CO2 Zeppelin
# downloaded 2020-08-19 from https://gaw.kishou.go.jp/search/file/0054-6001-1001-01-01-9999
# value:units : ppm
# value:long_name : measured_mole_fraction_of_trace_gas_in_dry_air
atm_co2 <-
  read_delim(file = paste0(path, "atmospheric_co2_zeppelin/co2_zep_surface-insitu_54_9999-9999_hourly.txt"),
  delim = " ",
  skip = 181,
  col_names = TRUE,
  na = "-999.999",
  ) %>%
  dplyr::mutate(pco2_air = value,
  datetime = as_datetime(paste(paste(year, month, day, sep="-"), paste(hour, minute, second, sep="-"), sep = " "))) %>%
  dplyr::select(datetime, pco2_air)
d_all <- dplyr::left_join(d_all, atm_co2, by = "datetime")
p_atm_co2 <- ggplot(data=atm_co2) +
  geom_point(aes(x = datetime, y = pco2_air), col = "blue", size = 0.15, na.rm = TRUE) +
  labs(title = "Atmospheric CO2 at Zeppelin", x = "Time", y = "CO2 (ppm)") +
  Mytheme(size_labs = 8)
ggsave(filename = "figures/atm_co2.png", plot = p_atm_co2, width = 20, units = "cm")
```

>>>>

```{r atmospheric CO2 Zeppelin, echo=FALSE, message= FALSE, warning=FALSE}
## Atmospheric CO2 Zeppelin
# downloaded 2020-08-19 from https://gaw.kishou.go.jp/search/file/0054-6001-1001-01-01-9999
# value:units : ppm
# value:long_name : measured_mole_fraction_of_trace_gas_in_dry_air
atm_co2 <-
  read_delim(file = paste0(path, "atmospheric_co2_zeppelin/co2_zep_surface-insitu_54_9999-9999_hourly.txt"),
  delim = " ",
  comment = "#",
  #skip = 182,
  col_names = TRUE,
  na = "-999.999",
  ) %>%
  dplyr::mutate(pco2_air = value,
  datetime = as_datetime(paste(paste(year, month, day, sep="-"), paste(hour, minute, second, sep="-"), sep = " "))) %>%
  dplyr::select(datetime, pco2_air)
d_all <- dplyr::left_join(d_all, atm_co2, by = "datetime")
p_atm_co2 <- ggplot(data=atm_co2) +
  geom_point(aes(x = datetime, y = pco2_air), col = "blue", size = 0.15, na.rm = TRUE) +
  labs(title = "Atmospheric CO2 at Zeppelin", x = "Time", y = "CO2 (ppm)") +
  Mytheme(size_labs = 8)
ggsave(filename = "figures/atm_co2.png", plot = p_atm_co2, width = 20, units = "cm")
```
